---
title: "Final Project Video Games"
author: "Tommy Lam, Eric Le, Maya Nair, Assaf Vayner"
date: "5/17/2020"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
source("scripts/summary_table.R")
source("scripts/summary_questions.R")
source("scripts/charts.R")
```

## Summary Information

### Which top 3 publishers sold the most games in North America, Europe, Japan, and globally?
One piece of information we were interested to look further into was what publishers were dominant in various regions as well as which publishers were dominant worldwide. In North America, the top 3 publishers in 2016 were `r vector3_to_string(na_publisher)`. Next, in Europe, the top 3 publishers were `r vector3_to_string(eu_publisher)`. Last, in Japan the top 3 publishers were `r vector3_to_string(jp_publisher)`. Overall, the top 3 publishers globally were `r vector3_to_string(global_publisher)`. Overall, it was interesting to see that Nintendo was one of the top publishers across the board.

### What are the top 3 game genres in a given region based on sales?
From our second question, we looked to find which genres were most popular in certain regions depending on the sales of various games. In North America, the top 3 genres were `r vector3_to_string(na_genres)`. In Japan, the top 3 genres were `r vector3_to_string(jp_genres)`. In Europe, the top 3 genres were `r vector3_to_string(eu_genres)`. Lastly, the top 3 genres worldwide, were `r vector3_to_string(global_genres)`. From this, we found that Action, Sports, and shooter games were prodominantly popular with one outlier being Role-Playing games in Japan.

### Do certain consoles get played more in certain regions?
Next, we sought to find which consoles of 2016 were most popular in given regions. In North America, the top 3 consoles were `r vector3_to_string(na_platform)`, in Japan, the top 3 consoles were `r vector3_to_string(jp_platform)`, and in Europe, the top 3 consoles were `r vector3_to_string(eu_platform)`. Interestingly enough, we found that the same consoles appeared to dominate overall no matter the region we analyzed. 

### What age restriction gets the least and most playtime?
Our next question we were interested in answering, is what age restriction had the least and most playtime on Steam. From this, we discovered that the age restriction with the least playtime on Steam was, `r least_play_time`, and the age restriction with the most playtime was `r most_play_time`.

### Are people playing more time on multiplayer games?
According to data collected regarding games on steam, there were `r steam_multiplayer_playtime$num_multi` multiplayer games (including online and local multiplayer games) out of `r steam_multiplayer_playtime$num_games` games. The average play time across all multiplayer games was `r steam_multiplayer_playtime$multiplayer_playtime` minutes while it was `r steam_multiplayer_playtime$non_multi_playtime` for non-multiplayer games showing that non-multiplayer games generally get played for longer by each owner.

## Table of Most Successful Publishers

The following table shows the `r nrow(publisher_table)` video game publishers sorted by Global Sales. These were the publishers who had global sales exceeding 2 standard deviations from the mean global sales of all publishers. The Global Popularity column is calculated by the reciprocal of the multiplication of the disparities between the NA, EU, JP and other Sales normalized to be from 0 to 1 by deviding by global sales. The Popularity Rank column helps to show which Publishers have higher Global Popularity values. The goal of this measurement is to show which video game publishers do well across all regions rather than in a single region. This shows that while `r publisher_table["Publisher", 1]` has greater over all Global Sales, `r highest_popularity_publisher` does a better job at selling their products across the world at more similar rate. The Sales values are included as is the Global Popularity score to present the actual differences in sales, and it is apparent from the tables that the publishers with sales numbers closer to each other have a lower popularity score and rank.

```{r, echo=FALSE}
kable(publisher_table,
      align = 'rccccccc',
      col.names = gsub("[_*]", " ", colnames(publisher_table)))
```

## Barchart Comparing Genres and Publisher

The following barcharts look at different genres to see which games and publishers sold the most globally. These barcharts looked at genre and global sales exceeding 3 standard deviations from the mean global sales in order to focus on the top performing games without cluttering the data. This barchart is included because it is clear to see which games performed the most and which publisher produced the games. The uage of color to differentiate publishers also adds to the clarity of the chart. The 2 genres that we tested were sports and shooter. For sports games, we can see that the top game sales are all from Nintendo and their Wii fit and Wii sports games. For shooter games, we can tell that Call of duty games from Activision made the most sum of money, but Duck Hunt actually beats out all of the other games when compared individually. 

```{r, echo=FALSE, fig.hold='hold', out.width="50%"}
sports_barchart

shooter_barchart
```

## Pie Chart Comparing Sales by Console

The following pie charts show a comparison between the amount of overall sales of games that are released on multiple platforms. The pie chart is split into different slices resembling sales on each platform the game is sold. This chart is included to clearly show the sales among platforms for specific games to clear inquiry regarding the many inputs of a certain game. Below are pie charts using the game Grand Theft Auto V and Call of Duty: Black Ops 3 as an example:

```{r, echo=FALSE, fig.hold='hold', out.width="50%"}
pie("Grand Theft Auto V")
pie("Call of Duty: Black Ops 3")
```

Some observations we could find in these pie charts are that the most copies of GTA V were sold on PS3 while the most copies of BO3 were sold on PS4.

## 3D Scatter plot of game sales

The following scatterplot is interactive to help see how well each game performed in specific regions and globally. For the axis, we have North American, Japan, and European sales, while having the color scale with global sales. We decided to do an interactive scatter plot for this part in order for the reader to see how the game sold in each region specifically, and the color scaling helps see which games did the best globally. While hovering over each dot, you can see the stats broken down along with name and genre. The filtered data was set to 6 standard deviations above the mean, but there are still many games so we can tell that there have been more games that performed worse than games that have been successful. We can see from the games that sold 25M +, the US contributed the most out of the regions tested and so we can tell that most of the game sales come from the US. The genres of popular games are also diverse being Platform, Puzzle, Shooter, and Role-playing so that means there is variety when it comes to popular games and not one genre is dominating the market.

```{r, echo=FALSE}
x3d_scatterplot
```